---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# flagfillr

flagfillr is a little package that makes it easier to use flags as fills (i.e. backgrounds) for [ggplot2](https://github.com/tidyverse/ggplot2) maps.  

## Installation

You can install flagfillr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("RobertMyles/flag_fillr")
```

<br>
**Important Note:** flagfillr works with ggplot2's `geom_sf()`, which is currently only available in the current development version of ggplot2 (version 2.2.1.9000).  

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## to do
-[] create repos of flag pngs 
-[] abstract process into function or perhaps package 
-[] blog post introducing the idea 
-[] blog post showing economic partners


## links
- merge this to passport? https://github.com/mledoze/countries

https://github.com/CivilServiceUSA/us-states

# dependent territories:
https://en.wikipedia.org/wiki/Gallery_of_flags_of_dependent_territories

# flags by country:
https://en.wikipedia.org/wiki/List_of_Argentine_flags (argentina)

## related
https://github.com/emphaticpuma/webflags